---
title: "Smartphone Use and Mental Health"
output: html_document
editor_options: 
  chunk_output_type: console
---

#Set Working Directory
```{r}
setwd("~/Desktop/Manuscripts/Smartphone Use and Mental Health")
```

# Load Packages_______________________________________
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(tidyr)
library(tidylog)
library(ggplot2)
library(dplyr)
library(psych)
library(lubridate)
library(summarytools)
library(styler)
library(readr)
library(janitor)

library(corrplot)
library(zoo)
library(magrittr)
library(readr)
library(naniar)
library(car)
library(reshape2)
library(jmv)

library(lme4) #for estimating multilevel models
library(lmerTest) #for p-values added to lme4 output
library(texreg) #for better outputs
library(effects) #for visualizing multilevel model effects
library(sjstats) #might have to manually add
library(sjPlot) #Print results
library(sjlabelled) #Allows for custom printed results
library(sjmisc)
library(r2mlm)
library(merTools)
library(DHARMa) #model fit for mlm
```

#Load Data
```{r}
ema_data1 <- data.table::fread("~/Desktop/Manuscripts/Smartphone Use and Mental Health/NT_TTP_DailyDiary.csv")

smartphone_data1 <- data.table::fread("~/Desktop/Manuscripts/Smartphone Use and Mental Health/neuroteen_ttp_screentime_merged 4.22.21.csv")

smartphone_data1 <- smartphone_data1 %>% 
  dplyr::select(-V1)

demographics <- data.table::fread("~/Desktop/Manuscripts/Smartphone Use and Mental Health/demographics.csv")
```

#Clean Data
##EMA Data Cleaning
###Select Variables
```{r}
ema_data2 <- ema_data1 %>% 
  dplyr::select(ID,
                PhoneType,
                DayofWeek,
                TypeofDay,
                Day,
                EMAType,
                Submitted,
                aSchoolDay,
                Date,
                StartTime,
                EndTime,
                Duration,
                aEmotToday1, #anxious
                aEmotToday4, #stress
                aEmotToday5, #happy
                aEmotToday9, #sad
                aEmotToday10, #lonely
                aSM, #Social Media: Did you use social media (e.g., Instagram, TikTok, Twitter, Facebook, YouTube, Reddit, or other sites) today?
                aSM1, #Social Media Usage: To fill up spare time because I was bored
                aSM2, #Social Media Usage: For entertainment
                aSM3, #Social Media Usage: To stay up to date with current events and news
                aSM4, #Social Media Usage: To connect with friends
                aSM5, #Social Media Usage: To share photos or videos
                aSM6, #Social Media Usage: To share my opinion
                aSM7, #Social Media Usage: To meet new people
                aSM8, #Social Media Usage: To get likes and positive feedback
                aSM9, #Social Media Usage: To browse my friends' profiles/content
                #aSM10, #Social Media Usage: To search and buy products
                aSM11, #Social Media Usage: To vent
                aSM12, #Social Media Usage: Other (please specify)
                aSM13, #Social Media Usage: Other (please specify)
                aSM_Feel, #Social Media: How did social media make you feel today?
                aSM_Mood1, #Social Media: How much did social media have a positive impact on your mood today?
                aSM_Mood2, #Social Media: How much did social media have a negative impact on your mood today?
                aSM_Time) %>%  #Social Media: How much total time did you spend using social media today?
  dplyr::rename(subject_id = ID,
                anxious = aEmotToday1,
                stress = aEmotToday4,
                happy = aEmotToday5,
                sad = aEmotToday9,
                lonely = aEmotToday10,
                pas_1 = aSM1,
                pas_2 = aSM2,
                pas_3 = aSM3,
                pas_4 = aSM9,
                act_1 = aSM4,
                act_2 = aSM5,
                act_3 = aSM6,
                act_4 = aSM7,
                act_5 = aSM8,
                #act_6 = aSM10,
                act_7 = aSM11) %>% 
  dplyr::filter(Submitted == 1)
```

###Label Factors
```{r}
ema_data2$PhoneType <- factor(ema_data2$PhoneType,
                            levels = c("1", "2"),
                            labels = c("iOS", "Android"))

ema_data2$aSchoolDay <- factor(ema_data2$aSchoolDay,
                            levels = c("1", "2", "3"),
                            labels = c("In Person School", "Virtual School", "No School"))

ema_data3 <- ema_data2[-158,]
```

###Add missing observations
```{r}
#This adds the missing day for any missing days for each participant
ema_data4 <- ema_data3 %>% 
  tidyr::complete(subject_id, Day = 0:14)

#Fill in Phone Type
ema_data4 <- ema_data4 %>% 
  fill("PhoneType")

ema_data4$Date <- lubridate::as_date(ema_data4$Date, format = "%m/%d/%Y")

ema_data5 <- ema_data4 %>% 
  mutate(Date = lubridate::as_date(Date),
         Date1 = lead(Date) - 1,
         Date2 = ifelse(is.na(Date), as.character(Date1), as.character(Date))) %>% 
  dplyr::select(-c(Date, Date1)) %>% 
  rename(Date = Date2)

ema_data5$Date <- lubridate::as_date(ema_data5$Date, format = "%Y-%m-%d")


#Create New Weekday Variable
ema_data5$weekday <- weekdays(ema_data5$Date)

#Create Weekday and Weekend Variable
ema_data5$TypeofDay <- ifelse(weekdays(ema_data5$Date) %in% c("Saturday", "Sunday"), "Weekend", "Weekday")

#Remove Old Variables
ema_data6 <- ema_data5 %>% 
  dplyr::select(-DayofWeek)
```

###Check Structure
```{r}
str(ema_data6)

#Make Variables Factor
#ema_data4[,2:8] <- lapply(ema_data4[,2:8], as.factor)
#ema_data4[,18:30] <- lapply(ema_data4[,18:30], as.factor)

#Make Variables Numeric
#ema_data4[,12:17] <- lapply(ema_data4[,12:17], as.numeric)
#ema_data4[,32:35] <- lapply(ema_data4[,32:35], as.numeric)

#Make Variables Factor
ema_data6[,1:7] <- lapply(ema_data6[,1:7], as.factor)
ema_data6[,34] <- lapply(ema_data6[,34], as.factor)


#Make Variables Numeric
ema_data6[,11:26] <- lapply(ema_data6[,11:26], as.numeric)
ema_data6[,29:31] <- lapply(ema_data6[,29:31], as.numeric)
ema_data6[,32] <- lapply(ema_data6[,32], as.numeric)
```

##Remove Variables
```{r}
ema_data6 <- ema_data6 %>% 
  dplyr::select(-c(aSM12, aSM13))
```

##Clean Smartphone
###Select Variables
```{r}
smartphone_data2 <- smartphone_data1 %>% 
  dplyr::select(subject_id,
                date,
                day,
                finished,
                correct_screenshot_screentime,
                correct_screenshot_pickups,
                correct_screenshot_notifications,
                time_limit,
                grey_screentime,
                unusual_night_use,
                total_screentime_hours,
                total_screentime_minutes,
                total_pickups,
                total_notifications) %>% 
  dplyr::filter(finished == 1,
                correct_screenshot_screentime == 1) %>% 
  dplyr::rename(Date = date,
                Day = day)
```

###Merge Screentime Hours and Minutes Columns
####Turn Screentime Hours Column to Minutes
```{r}
smartphone_data2$total_screentime_hours_to_min <- smartphone_data2$total_screentime_hours*60
```

####Add New Minutes Column to Minutes
```{r}
smartphone_data3 <- smartphone_data2 %>% 
  dplyr::rowwise() %>% 
  mutate(smartphone_total_min = sum(total_screentime_minutes, total_screentime_hours_to_min, na.rm = TRUE)) %>% 
  dplyr::select(-c(total_screentime_minutes, total_screentime_hours, total_screentime_hours_to_min))

smartphone_data3$sad_log10 <- smartphone_data3$smartphone_total_min/60
```

##Check Structure
```{r}
str(smartphone_data3)

smartphone_data3$Date <- as.Date(smartphone_data3$Date, format = "%m/%d/%y")

smartphone_data3$Day <- as.factor(smartphone_data3$Day)
```

##Merge Data
```{r}
data1 <- full_join(ema_data6, smartphone_data3, by = c("subject_id", "Day", "Date"))
```

##Create Active vs Passive Variable
```{r}
#Recode from 2 and 1 to 1 and 0

data1$act_1[data1$act_1 == 1] <- 0
data1$act_1[data1$act_1 == 2] <- 1
data1$act_2[data1$act_2 == 1] <- 0
data1$act_2[data1$act_2 == 2] <- 1
data1$act_3[data1$act_3 == 1] <- 0
data1$act_3[data1$act_3 == 2] <- 1
data1$act_4[data1$act_4 == 1] <- 0
data1$act_4[data1$act_4 == 2] <- 1
data1$act_5[data1$act_5 == 1] <- 0
data1$act_5[data1$act_5 == 2] <- 1
data1$act_7[data1$act_7 == 1] <- 0
data1$act_7[data1$act_7 == 2] <- 1

data1$pas_1[data1$pas_1 == 1] <- 0
data1$pas_1[data1$pas_1 == 2] <- 1
data1$pas_2[data1$pas_2 == 1] <- 0
data1$pas_2[data1$pas_2 == 2] <- 1
data1$pas_3[data1$pas_3 == 1] <- 0
data1$pas_3[data1$pas_3 == 2] <- 1
data1$pas_4[data1$pas_4 == 1] <- 0
data1$pas_4[data1$pas_4 == 2] <- 1

data2 <- data1 %>% 
  dplyr::rowwise() %>% 
  mutate(act_total = sum(act_1, act_2, act_3, act_4, act_5, act_7)) %>% 
  mutate(pas_total = sum(pas_1, pas_2, pas_3, pas_4)) %>% 
  mutate(type_of_use = case_when(
      pas_total <= 0 & act_total <= 0 ~ 0,
      pas_total > 0 & act_total <= 0 ~ 1,
      pas_total <= 0 & act_total > 0 ~ 2,
      pas_total > 0 & act_total > 0 ~ 3))
  
```

#Select Final Variables
```{r}
data3 <- data2 %>% 
  dplyr::select(subject_id,
                Day,
                TypeofDay,
                PhoneType,
                anxious,
                stress,
                happy,
                sad,
                lonely,
                type_of_use,
                grey_screentime,
                unusual_night_use,
                sad_log10)
```

#Merge
```{r}
data4 <- left_join(data3, demographics, by = "subject_id")

data4 <- data4 %>% 
  dplyr::select(-V1)
data4$age
data4$gender <- as.factor(data4$gender)
data4$race <- as.factor(data4$race)
data4$age <- as.numeric(data4$age)
data4$smfq <- as.numeric(data4$smfq)

data4 <- as.data.frame(data4)

str(data4)
```


##Check Missing Data
```{r}
#Overall missing data
data4 %>% 
  naniar::vis_miss()

#Combination of missing data
data4 %>% 
  naniar::gg_miss_upset()

#Count of missing data
naniar::gg_miss_var(data4, Day)
```

#Remove Participant
```{r}
data5 <- data4 %>% 
  dplyr::filter(subject_id != "P70")
```

#Imputation
```{r}
set.seed(123)

all_imputations <- mice::mice(data5, maxit= 10, m = 10)

#all_imputations <- mice::complete(all_imputations, "long")

merged_imputations1 <- sjmisc::merge_imputations(
  data5,
  all_imputations,
  ori = data5,
  summary = c("none", "dens", "hist", "sd"),
  filter = NULL
)
```



#Create Lagged Variables
```{r}
#Create Next Day Smartphone Minutes and Hours
merged_imputations2 <- merged_imputations1 %>% 
  group_by(subject_id) %>% 
  mutate(sad_log10_lead1 = lead(sad_log10_imp, n = 1),
         sad_log10_lead2 = lead(sad_log10_imp, n = 2))

#Create Next Day Affect
final_imputations <- merged_imputations2 %>% 
  group_by(subject_id) %>% 
  mutate(anxiety_lead1 = lead(anxious_imp, n = 1),
         anxiety_lead2 = lead(anxious_imp, n = 2),
         stress_lead1 = lead(stress_imp, n = 1),
         stress_lead2 = lead(stress_imp, n = 2),
         sad_lead1 = lead(sad_imp, n = 1),
         sad_lead2 = lead(sad_imp, n = 2),
         lonely_lead1 = lead(lonely_imp, n = 1),
         lonely_lead2 = lead(lonely_imp, n = 2),
         sad_log10_lead1 = lead(sad_log10, n = 1),
         sad_log10_lead2 = lead(sad_log10, n = 2))
```

###Add Missing Day of Week and Date
```{r eval=FALSE, include=FALSE}
#data2 <- data1 %>% 
#  tidyr::complete(subject_id, nesting(Day, DayofWeek), fill = list(DayofWeek = c("Monday", 
#                                                                        "Tuesday", 
#                                                                        "Wednesday", 
#                                                                        "Thursday", 
#                                                                        "Friday", 
#                                                                        "Saturday", 
#                                                                        "Sunday")))
```

##Descriptives
```{r}
describeBy(final_imputations)

final_imputations$sad_log10 <- log(final_imputations$sad_imp)
final_imputations$sad_lead1_log10 <- log(final_imputations$sad_lead1)
final_imputations$sad_lead2_log10 <- log(final_imputations$sad_lead2)
final_imputations$anxious_log10 <- log(final_imputations$anxious_imp)
final_imputations$anxiety_lead1_log10 <- log(final_imputations$anxiety_lead1)
final_imputations$anxiety_lead2_log10 <- log(final_imputations$anxiety_lead2)
final_imputations$lonely_log10 <- log(final_imputations$lonely_imp)
final_imputations$lonely_lead1_log10 <- log(final_imputations$lonely_lead1)
final_imputations$lonely_lead2_log10 <- log(final_imputations$lonely_lead2)

final_imputations$subject_id <- as.factor(final_imputations$subject_id)
```

###Plot
```{r}
#Sad
hist(data1$sad)
boxplot(data1$sad)

#Sad
hist(data1$lonely)
boxplot(data1$lonely)

#Smartphone Use Hours
hist(data1$sad_log10)
boxplot(data1$sad_log10)

#Pickups
hist(data1$total_pickups)
boxplot(data1$total_pickups)

#Notifications
hist(data1$total_notifications)
boxplot(data1$total_notifications)
```

#Load Functions
```{r}
#Singular means you haven a variance component that is sitting on 0. It may or may not impact estimates. Should figure out if you threw something in the model that is not useful
check_singularity <- function(lmerobj) {
  tt <- getME(lmerobj,"theta") #RE estimates
  ll <- getME(lmerobj,"lower") #lower bound on estimate
  
  #look for RE estimates that are very small (near zero) and the lower bound encompasses 0
  low_re <- tt[ll==0 & tt < 1e-2]
  return(low_re)
}
```



#Analyses
##Create Between and Within Person Terms
```{r}
final_imputations <- bmlm::isolate(final_imputations, by = "subject_id",
             value = c("sad_log10", "sad_log10_lead1", "sad_log10", "sad_lead1_log10", "sad_lead2_log10", "stress", "anxious_log10", "happy", "lonely_log10"),
             which = "both")
```

##Concurrent Models
###Smartphone to Sad
```{r}
#Random Intercept and Fixed Slope
concurrent_model_sad1 <- lmer(sad_log10 ~ 1 + smartphone_total_hours_cb + smartphone_total_hours_cw + (1 | subject_id), REML = TRUE, data = final_imputations)
summary(concurrent_model_sad1)

#Random Intercept and Slope
concurrent_model_sad2 <- lmer(sad_log10 ~ 1 + smartphone_total_hours_cb + smartphone_total_hours_cw + (1 + smartphone_total_hours_cw | subject_id), REML = TRUE, data = final_imputations, control = lmerControl(optimizer ="Nelder_Mead"))
summary(concurrent_model_sad2)
check_singularity(concurrent_model_sad2) #Smartphone within subjects

#Add Demographics
concurrent_model_sad3 <- lmer(sad_log10 ~ 1 + smartphone_total_hours_cb + smartphone_total_hours_cw + age_imp + gender_imp + race_imp + (1 | subject_id), REML = TRUE, data = final_imputations)
summary(concurrent_model_sad3)

#Add Interactions
concurrent_model_sad4 <- lmer(sad_log10 ~ 1 + smartphone_total_hours_cb*smfq_imp + smartphone_total_hours_cw*smfq_imp + smartphone_total_hours_cb*digital_pressure_imp + smartphone_total_hours_cw*digital_pressure_imp + age_imp + gender_imp + race_imp + (1 | subject_id), REML = TRUE, data = final_imputations)
summary(concurrent_model_sad4)



#Compare Model Fit
anova(concurrent_model_sad1, concurrent_model_sad2, concurrent_model_sad3, concurrent_model_sad4) #Same Model Fit
performance::compare_performance(concurrent_model_sad1, concurrent_model_sad2, concurrent_model_sad3, concurrent_model_sad4, rank = TRUE) #Use random intercept model and slope
plot(performance::compare_performance(concurrent_model_sad1, concurrent_model_sad2, concurrent_model_sad3, concurrent_model_sad4, rank = TRUE))
```

###Sad to Smartphone
```{r}
#Random Intercept and Fixed Slope
concurrent_model_smartphone1 <- lmer(smartphone_total_hours ~ 1 + sad_log10_cb + sad_log10_cw + (1 | subject_id), REML = TRUE, data = final_imputations)
summary(concurrent_model_smartphone1)

#Random Intercept and Slope
concurrent_model_smartphone2 <- lmer(smartphone_total_hours ~ 1 + sad_log10_cb + sad_log10_cw + (1 + sad_log10_cw | subject_id), REML = TRUE, data = final_imputations, control = lmerControl(optimizer ="Nelder_Mead"))
summary(concurrent_model_smartphone2)
check_singularity(concurrent_model_smartphone2) #Smartphone within subjects

#Add Demographics
concurrent_model_smartphone3 <- lmer(smartphone_total_hours ~ 1 + sad_log10_cb + sad_log10_cw + age_imp + gender_imp + race_imp + (1 | subject_id), REML = TRUE, data = final_imputations)
summary(concurrent_model_smartphone3)

#Add Interactions
concurrent_model_smartphone4 <- lmer(smartphone_total_hours ~ 1 + sad_log10_cb*smfq_imp + sad_log10_cw*smfq_imp + sad_log10_cb*digital_pressure_imp + sad_log10_cw*digital_pressure_imp + age_imp + gender_imp + race_imp + (1 | subject_id), REML = TRUE, data = final_imputations)
summary(concurrent_model_smartphone4)
check_singularity(concurrent_model_smartphone2)



#Compare Model Fit
anova(concurrent_model_smartphone1, concurrent_model_smartphone2, concurrent_model_smartphone3, concurrent_model_smartphone4) #Same Model Fit
performance::compare_performance(concurrent_model_smartphone1, concurrent_model_smartphone2, concurrent_model_smartphone3, concurrent_model_smartphone4, rank = TRUE) #Use random intercept model and slope
plot(performance::compare_performance(concurrent_model_smartphone1, concurrent_model_smartphone2, concurrent_model_smartphone3, concurrent_model_smartphone4, rank = TRUE))
```

##Lagged Models
###Smartphone to Sad
```{r}
lagged_model_sad1 <- lmer(sad_lead1_log10 ~ 1 + sad_log10 + smartphone_total_hours_cb + smartphone_total_hours_cw + (1 | subject_id), REML = TRUE, data = final_imputations)
summary(lagged_model_sad1)

lagged_model_sad2 <- lmer(sad_lead1_log10 ~ 1 + sad_log10 + smartphone_total_hours_cb + smartphone_total_hours_cw + (1 + smartphone_total_hours_cw | subject_id) , REML = TRUE, data = final_imputations)
summary(lagged_model_sad2)
check_singularity(lagged_model_sad2)

lagged_model_sad3 <- lmer(sad_lead1_log10 ~ 1 + sad_log10 + smartphone_total_hours_cb + smartphone_total_hours_cw + age_imp + gender_imp + race_imp + (1 | subject_id), REML = TRUE, data = final_imputations)
summary(lagged_model_sad3)

lagged_model_sad4 <- lmer(sad_lead1_log10 ~ 1 + sad_log10*smfq_imp + smartphone_total_hours_cb*smfq_imp + smartphone_total_hours_cw*smfq_imp + sad_log10*digital_pressure_imp + smartphone_total_hours_cb*digital_pressure_imp + smartphone_total_hours_cw*digital_pressure_imp + age_imp + gender_imp + race_imp + (1 | subject_id), REML = TRUE, data = final_imputations)
summary(lagged_model_sad4)






anova(lagged_model_sad1, lagged_model_sad2, lagged_model_sad3, lagged_model_sad4)
performance::compare_performance(lagged_model_sad1, lagged_model_sad2, lagged_model_sad3, lagged_model_sad4, rank = TRUE) #Use random intercept and slope model
plot(performance::compare_performance(lagged_model_sad1, lagged_model_sad2, lagged_model_sad3, lagged_model_sad4, rank = TRUE))
```

###Sad to Smartphone
```{r}
lagged_model_smartphone1 <- lmer(smartphone_total_hours_lead1 ~ 1 + smartphone_total_hours + sad_log10_cb + sad_log10_cw + (1 | subject_id), REML = TRUE, data = final_imputations)
summary(lagged_model_smartphone1)
check_singularity(lagged_model_smartphone1)

lagged_model_smartphone2 <- lmer(smartphone_total_hours_lead1 ~ 1 + smartphone_total_hours + sad_log10_cb + sad_log10_cw + (1 + sad_log10_cw | subject_id), REML = TRUE, data = final_imputations)
summary(lagged_model_smartphone2)

lagged_model_smartphone3 <- lmer(smartphone_total_hours_lead1 ~ 1 + smartphone_total_hours + sad_log10_cb + sad_log10_cw + age_imp + gender_imp + race_imp + (1 + sad_log10_cw | subject_id), REML = TRUE, data = final_imputations)
summary(lagged_model_smartphone3)

lagged_model_smartphone4 <- lmer(smartphone_total_hours_lead1 ~ 1 + smartphone_total_hours*smfq_imp + sad_log10_cb*smfq_imp + sad_log10_cw*smfq_imp + smartphone_total_hours*digital_pressure_imp + sad_log10_cb*digital_pressure_imp + sad_log10_cw*digital_pressure_imp + age_imp + gender_imp + race_imp + (1  | subject_id), REML = TRUE, data = final_imputations)
summary(lagged_model_smartphone4)

anova(lagged_model_smartphone1, lagged_model_smartphone2, lagged_model_smartphone3, lagged_model_smartphone4)
performance::compare_performance(lagged_model_smartphone1, lagged_model_smartphone2, lagged_model_smartphone3, lagged_model_smartphone4, rank = TRUE) #Use random intercept and slope model
plot(performance::compare_performance(lagged_model_smartphone1, lagged_model_smartphone2, lagged_model_smartphone3, lagged_model_smartphone4, rank = TRUE))
```

#Graph Covariation
##Convert variables to Z-Score
```{r}
graph_data <- final_imputations %>% 
  dplyr::select(subject_id,
                Day,
                sad_log10,
                smartphone_total_hours_imp)

graph_data$sad_log10_zscore <- scale(graph_data$sad_log10)
graph_data$smartphone_zscore <- scale(graph_data$smartphone_total_hours_imp)


str(graph_data)
```

##Turn Data Into Long
```{r}
graph_data2 <- graph_data %>%  
  pivot_longer(cols = c(sad_log10_zscore, smartphone_zscore), names_to = "variable", values_to = "value")

str(graph_data2)
graph_data2$variable <- as.factor(graph_data2$variable)
graph_data2$Day <- as.numeric(graph_data2$Day)
```


##Graph
```{r}
#Plot Smartphone Use and Sadness
smartphone_sad_graph1 <- ggplot(data=subset(graph_data2), aes(x = Day, y = value, color = variable)) +
  #geom_line(aes(group = SID), alpha = .1) + #This fades the individual lines
  stat_summary(data=subset(graph_data2), aes(group=variable), fun=mean, geom="smooth") + 
  theme(axis.ticks = element_line(colour = "black"), 
    panel.grid.major = element_line(colour = "white"), 
    panel.grid.minor = element_line(colour = "white"), 
    axis.title = element_text(size = 10), 
    axis.text = element_text(size = 10, colour = "black"), 
    axis.text.x = element_text(colour = "black"), 
    axis.text.y = element_text(colour = "black"), 
    plot.title = element_text(size = 10), 
    legend.text = element_text(size = 10), 
    legend.title = element_text(size = 10), 
    panel.background = element_rect(fill = "white"), 
    legend.key = element_rect(fill = "white"), 
    legend.background = element_rect(fill = "white")) +
  labs(title = "Covariation of Smartphone Use and Sadness", x = "Day", y = "Value (Z-Scored)", colour = "Variable")

smartphone_sad_graph1 + gganimate::transition_reveal(Day)

gganimate::anim_save("smartphone_sadness_covariation.gif")
```










